\textbf{ Accurate spectrophotometric estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-30 paper/sp.tex
note to self
notes to self; acks
fixing up a bit the data section

\shorttitle{spectrophotometric distance estimates}
\shortauthors{eilers, hogg, rix}
%\watermark{kittens}

@@

@@

ACE: We match the \apogee\ stars making the $\logg$ cut also to
the \zmass\ ACE WHICH CATALOG by ACE WHAT CRITERION?
This gives, for each matching star $n$,
near-infrared photometry $J_n$, $H_n$, and $K_n$.
In detail we use from the catalog the entries ACE WHAT SPECIFIC CATALOG ENTRIES.

ACE: We match the \apogee+\zmass\ stars to he \wise\ ACE WHICH CATALOG by ACE WHAT CRITERION?
This gives, fore each matching star $n$,
mid-infrared photometry $W_{1n}$ and $W_{2n}$ at ACE WHAT WAVELENGTHS?
In detail we use the ACE WHAT SPECIFIC CATALOG ENTRIES?

@@

For each star $n$, we take from \gaia\ DR2 we the parallax $\varpi_n$
and its uncertainty $\sigma_{\varpi n}$, which will be used in
constructing the inverse-root-luminosity $Q_n$ and associated
uncertainty $\sigma_n$.
Importantly, to each \gaia\ parallax measurement we add a positive
offset of $0.029$\,mas to adjust for the under-estimation of
parallaxes reported by the \gaia\ Collaboration (HOGG CITE LINDEGREN).
We also take from the \gaia\ data the photometric data $G_n$
(\code{phot_g_mean_mag}) and $G_{Bn}-G_{Rn}$ (\code{bp_rp}), which will
become part of the feature vector $x_n$.
We do not use the entire \gaia\ \acronym{DR2} Catalog but instead the subset
that meets ACE WHAT ADDITIONAL PHOTOMETRIC CUTS?

@@

For training, we need A and B Training Sets.
We define the Training Set stars to be Parent Sample stars that also
have a measured \gaia\ parallax.
The Training-Set stars, in addition to meeting all Parent-Sample cuts,
also must meet ACE WHAT ADDITIONAL CUTS to ensure that the parallax
measurements are good.
The training sets are shown in HOGG WHAT FIGURES?

But---as we have emphasized above---we do not cut ever on parallax or
parallax error or their ratio. For this reason, most of the training set
do not have significantly measured parallaxes and HOGG percent even have
negative parallaxes!
But we will perform our training such that it will be unbiased in these
circumstances.
Indeed it would be necessarily biased if ever we did cut on parallax or
parallax signal-to-noise.

@@

>>>>

\shorttitle{spectrophotometric distance estimates}
\shortauthors{hogg, eilers, rix}
%\watermark{kittens}

@@

HOGG: PUT WORDS HERE ABOUT GOING TWO-FOLD to pre-flash that we are going to do that
in the next Section.

@@

Because the \apogee\ target selection is based on \zmass, every \apogee\ star
comes with \zmass photometry.
That is, for each star $n$,
we have near-infrared photometry $J_n$, $H_n$, and $K_n$.
In detail we use from the catalog the entries ACE WHAT SPECIFIC CATALOG ENTRIES.

ACE: We match the \apogee+\zmass\ stars to he \wise\ ACE WHICH CATALOG by ACE WHAT CRITERION?
This gives, fore each matching star $n$,
mid-infrared photometry $W_{1n}$ and $W_{2n}$ at 3.6 and 4.5\,$\mu$m
In detail we use the ACE WHAT SPECIFIC CATALOG ENTRIES?

@@

We take from the \gaia\ \acronym{DR2} Catalog the photometric data $G_n$
(\code{phot_g_mean_mag}) and $G_{Bn}-G_{Rn}$ (\code{bp_rp}), which will
become part of the feature vector $x_n$.
We do not use the entire \gaia\ \acronym{DR2} Catalog but instead the subset
that meets ACE WHAT ADDITIONAL PHOTOMETRIC CUTS?

@@

For training, we need A and B Training Sets.
We define the Training Set stars to be Parent Sample stars that also
have a measured \gaia\ parallax.
The Training-Set stars, in addition to meeting all Parent-Sample cuts,
also must meet ACE WHAT ADDITIONAL CUTS to ensure that the parallax
measurements are good.
But---as we have emphasized above---we do not cut ever on parallax or
parallax error or their ratio. For this reason, most of the training set
do not have significantly measured parallaxes and HOGG percent even have
negative parallaxes!
But we will perform our training such that it will be unbiased in these
circumstances.
Indeed it would be necessarily biased if ever we did cut on parallax or
parallax signal-to-noise.

In detail,
for each star $n$ in the Training Sets, we take from \gaia\ DR2 we the parallax $\varpi_n$
and its uncertainty $\sigma_{\varpi n}$, which will be used in
constructing the inverse-root-luminosity $Q_n$ and associated
uncertainty $\sigma_n$.
Importantly, to each \gaia\ parallax measurement we add a positive
offset of $0.029$\,mas to adjust for the under-estimation of
parallaxes reported by the \gaia\ Collaboration (HOGG CITE LINDEGREN).
The training sets are shown in HOGG WHAT FIGURES?

@@

\wise\ Acknowledgement?

\project{\acronym{SDSS-IV}} ack.
